---
title: "R Markdown and Leaflet"
author: "Bekir YILDIZ"
date: "December 17, 2018"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

### Data plotted
The datasource used is from http://worldpopulationreview.com/countries/turkey-population/cities/

It shows the top five populated cities in Turkey.

```{r}
if(Sys.info()['sysname'] == "Windows") 
{
  setwd("D:/Dropbox (GSC)/SHELTERNFI IM/RScripts/Test/")
} else 
{
  setwd("/Users/bekir/Dropbox (GSC)/SHELTERNFI IM/RScripts/Test/")
}

library("leaflet")
data <- read.csv(file="City.csv", header=TRUE)
head(data)

map <- data %>%
        leaflet() %>%
        addTiles() %>%
        setView(lng = 35.2433, lat = 38.9637, zoom = 5) %>%
        addMarkers(popup = paste("City: ", data$City, "<br>",
                                 "Population: ", data$Population), 
        lng = data$Longitude, lat = data$Latitude)%>% 
        addCircles(weight=1,radius=data$Population/100)

map
```


